A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-02-12 manuscript.Rmd
add section on contributor covenant

This will create a file with the name `README.Rmd`.
When you knit this file, it in turn creates a `README.md`.
That means you can include R code or plots etc. within the readme.
The `README.md` file will look pleasant in the webbrowser, just like in Figure \@ref(fig:idea-change).

```{r readme-screenshot, include=FALSE}
# unfortunately css selectors won't work for pdf so we'll use png instead
readme <- here::here("images", "readme.png")
webshot2::webshot("https://github.com/aaronpeikert/repro-tutorial/",
                  file = readme,
                  selector = "div#readme", # only select file change
                  zoom = 1)# higher resolution
```

@@

Even when other researchers are excited to use your code or materials, they are usually legally inhibited from to doing so.
That is because in many countries (i.e. the USA) the creator of something has exclusive right to use their creation.
A license allows other people to use what you have created.
<!---exact copy from our previous manuscript, do we need to change? -->
In our experience, the [Creative Commons - Attribution license (CC-BY)](https://creativecommons.org/licenses/by/4.0/) is often appropriate for sharing texts, R Markdown files, generated figures, and other media, whereas scripts and any other computer code are often best shared under the [MIT license](https://opensource.org/licenses/MIT) (or similar permissive licenses).
Both licenses assure maximal freedom for future users while requiring the attribution of the original authors in derivative work.
These licenses are also in line with the recommendations by the Reproducible Research Standard [@stoddenEnhancingReproducibilityComputational2016; @stoddenEnablingReproducibleResearch2009].
A great resource to choose a license is [choosealicense.com](https://choosealicense.com), however, no resource, including our recommendation, replaces legal advice.
<!-- plagiary end -->
It is important to get written consent from collaborators when you change/add the license.
However, if they contribute to the project, after you have added a license, they give their consent by contributing.
To add a license to your project simply run:

@@

>>>>

This will create a file with the name `README.Rmd`.
When you knit this file, it in turn creates a `README.md`.
That means you can include R code or plots etc. within the readme.
The `README.md` file will look pleasant in the browser, just like in Figure \@ref(fig:idea-change).

```{r readme-screenshot, include=FALSE}
# unfortunately css selectors won't work for pdf so we'll use png instead
readme <- here::here("images", "readme.png")
webshot2::webshot("https://github.com/aaronpeikert/repro-tutorial/",
                  file = readme,
                  selector = "div#readme",
                  zoom = 1)# higher resolution
```

@@

Even when other researchers are excited to use your code or materials, they are usually legally inhibited from to doing so.
That is because in many countries (i.e. the USA) the creator of something has exclusive right to use their creation.
A license allows other people to use what you have created.
<!---exact copy from our previous manuscript, do we need to change? -->
In our experience, the [Creative Commons - Attribution license (CC-BY)](https://creativecommons.org/licenses/by/4.0/) is often appropriate for sharing texts, R Markdown files, generated figures, and other media, whereas scripts and any other computer code are often best shared under the [MIT license](https://opensource.org/licenses/MIT) (or similar permissive licenses).
Both licenses assure maximal freedom for future users while requiring the attribution of the original authors in derivative work.
These licenses are also in line with the recommendations by the Reproducible Research Standard [@stoddenEnhancingReproducibilityComputational2016; @stoddenEnablingReproducibleResearch2009].
A great resource to choose a license is [choosealicense.com](https://choosealicense.com), however, no resource, including our recommendation, replaces legal advice.
<!-- plagiary end -->
It is important to get written consent from collaborators when you change/add the license.
However, if their first contribution occurs after you have added a license, they give their consent by contributing.
To add a CC-BY license to your project simply run (there are similar commands for other licenses):

@@

We strongly suggest that you strive for respectful interactions with anyone who might want to contribute.
In fact, we hope it comes naturally to you.
To communicate that contributors can expect a welcoming and respectful environment, you can add the `r link( "https://www.contributor-covenant.org", "Contributor Covenant")`.
The Contributor Covenant is the code of conduct used by many open source project.
Contributing to an open project is daunting and a public pledge to value any contributions (even when you do not incorporate them) can help others to take the first step.

To add the Contributor Covenant to your project use:
